Tracing the Meta-Level: PyPy's Tracing JIT Compiler

### 2009-04-08 talk/icooolps2009/paper.tex
Typo typo.

The results show that the tracing JIT speeds up the execution of this Python
function significantly, even outperforming CPython. To achieve this, the tracer
traces through the whole Python dispatching machinery, automatically inlining
the relevant fast paths. However, the manually tuned Psyco still performs a lot
better than our prototype (although it is interesting to note that Psyco
improves the speed of CPython by only a factor 3.29 in this example, while
our tracing JIT improves PyPy by a factor 6.54).

>>>>

The results show that the tracing JIT speeds up the execution of this Python
function significantly, even outperforming CPython. To achieve this, the tracer
traces through the whole Python dispatching machinery, automatically inlining
the relevant fast paths. However, the manually tuned Psyco still performs a lot
better than our prototype (although it is interesting to note that Psyco
improves the speed of CPython by only a factor of 3.29 in this example, while
our tracing JIT improves PyPy by a factor of 6.54).
